EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
comparison with manual tests

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, four tools competed on a set of open source Java
classes. This paper describes the results of applying the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst17competition}.  In this
competition, \EVOSUITE achieved a 1457.3 overall score, which was the
highest among the competing tools.

@@

% overall results
Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage is generally in the expected range, with clear
increases for higher time budgets as expected, except for
$budget=300s$, where a decrease is observed, possibly due to crashes
or \emph{out-of-memory} errors\TODO{confirm this conjecture}. With
$budget=480s$, the average branch coverage achieved was \AvgCovG
(slightly higher than last year's $65.6\%$) and the average mutation
score was \AvgMutG (considerably higher than last year's $41.0\%$).

@@

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
\FlakyRandoop by Randoop). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.

@@

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
%\def\IEEEbibitemsep{6pt}

\bibliographystyle{IEEEtranS}
\bibliography{papers}
\balance

>>>>

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, four tools competed on a set of open source Java
classes. This paper describes the results of applying the \EVOSUITE
test generation tool~\cite{FrA11c} in this competition. Details about
the procedure of the competition, the technical framework, and the
benchmark classes can be found in~\cite{sbst17competition}.  In this
competition, \EVOSUITE achieved a 1457.3 overall score, which was the
highest among the competing and baseline tools.

@@

\subsection{Overall results}

Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage is generally in the expected range, with clear
overall increases for higher time budgets. With $budget=480s$, the
average branch coverage achieved was \AvgCovG (slightly higher than
last year's $65.6\%$) and the average mutation score was \AvgMutG
(considerably higher than last year's $41.0\%$).

This year, the contest also included manually written test suites as
baseline. \EVOSUITE significantly outperformed this manual baseline as
well, both in terms of branch coverage (avg. \AvgCovEvosuite vs
\AvgCovManual, with Vargha-Delaney's $A_{12}=\EvoManCovA$ and
$p\EvoManCovPV$) and mutation scores (avg. \AvgMutEvosuite vs
\AvgMutManual, with $A_{12}=\EvoManMutA$ and
$p\EvoManMutPV$).\TODO{Does showing A12 make sense if there's only one
  manual test suite per benchmark?}

@@

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
\FlakyRandoop by Randoop). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.

\subsection{Challenges}

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suite for benchmarks JXPATH-7 and
OKHTTP-8, and also struggled often for benchmarks LA4J-3, LA4J-7,
BCEL-9 (highlighted in Table~\ref{table:results}).\TODO{look into details}

% Look at benchmarks where coverage decreased with increased budget
Although coverage generally increased with higher time budgets, there
are instances where this expected behaviour was not observed,
specially for $budget=300s$, where the average across benchmarks
decreased. This is possibly due to crashes or out-of-memory
runtime errors.\TODO{confirm this conjecture}\TODO{look into details}

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively).\TODO{look into details}

@@

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
%\def\IEEEbibitemsep{6pt}
\clearpage
\bibliographystyle{IEEEtranS}
\bibliography{papers}
\balance
